---
title: "ML-Assignment4"
author: "Harish Kunaparaju"
date: "2022-11-05"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(factoextra) # clustering algorithms & visualization
library(ISLR)
library(caret)
```

#Importing the dataset
```{r}
Input <- read.csv("Pharmaceuticals.csv")
```

# a. Use only the numerical variables (1 to 9) to cluster the 21 firms. Justify the various choices made in conducting the cluster analysis, such as weights for different variables, the specific clustering algorithm(s) used, the number of clusters formed, and so on.

#Remove missing data and rescale variables for comparability before clustering data.
```{r}
PS<- na.omit(Input) #gives the data after removing the missing values.
PS
```

#To cluster the 21 firms, just the quantitative variables (1-9) need be collected.
```{r}
row.names(PS)<- PS[,1]
PS1<- PS[,3:11]
head(PS1)
```

#Scale all the dataframe's quantitative variables
```{r}
PS2<-scale(PS1)
head(PS2)
```

##Determining the no of clusters to do the cluster analysis using Elbow Method
```{r}
fviz_nbclust(PS2, kmeans, method = "wss") + labs(subtitle = "Elbow Method")
```

##Using Silhouette method for determining no of clusters
```{r}
fviz_nbclust(PS2, kmeans, method = "silhouette")+ labs(subtitle = "Silhouette Method")
```

The number of clusters is 5 in the above plots, which is sufficient to display the data 
variations.

```{r}
set.seed(60000)
k5<- kmeans(PS2,centers=5,nstart = 25) 
```

#Visualizing the output
```{r}
k5$centers  #for centroids
fviz_cluster(k5,data = PS2) # to Visualize the clusters
k5
distance<- dist(PS2, method = "euclidean")
fviz_dist(distance)
```
#Using K-Means Cluster Analysis-  to Fit the data with 5 clusters
```{r}
fit<-kmeans(PS2,5)
```

#calculating the mean of all quantitative variables in each cluster
```{r}
aggregate(PS2,by=list(fit$cluster),FUN=mean)
```

```{r}
PS3<-data.frame(PS2,fit$cluster)
head(PS3)
```

#view of the cluster plot
```{r}
library(cluster)
clusplot(PS2,fit$cluster,color = TRUE,shade = TRUE,labels = 2,lines = 0)
```


#b.Interpret the clusters with respect to the numerical variables used in forming the clusters.
By looking at the mean values of all quantitative variables in each cluster.

Cluster 1 - has highest Market_cap,ROA,ROE,Asset_Turnover and lowest is Beta,PE_Ratio.

Cluster 2 - has highest Rev_Growth and lowest PE_Ratio, Asset_Turnover.

Cluster 3 - has highest Beta, Leverage and lowest Market_Cap, ROE, ROA, Leverage, Rev_Growth, Net_Profit_Margin.

Cluster 4 - has highest PE_Ratio and lowest Leverage, Asset_Turnover.

Cluster 5 - has highest Net_Profit_Margin and lowest leverage,Beta. 

# c.s there a pattern in the clusters with respect to the numerical variables (10 to 12)? (those not used in forming the clusters)  
With respect to the Media recommendation variable, there is a pattern in the clusters.

Cluster 1 with highest Market_Cap, highest ROE, highest ROA, highest Asset_Turnover has equal Hold and Moderate Buy Recommendation.

Cluster 2 with lowest PE_Ratio and lowest Asset_Turnover has Hold Recommendation.

Cluster-3 with highest Beta, highest Leverage has mostly Moderate Buy Recommendation.

Cluster 4 with highest PE_Ratio has Hold Recommendation.

Cluster 5 with highest Net_Profit_Margin has mostly Hold Recommendation.

In terms of variables in clusters (10 to 12).

Clusters 1,3 has mostly Moderate Buy Recommendation.

Clusters 1,2,4,5 has Hold Recommendation.

# d.Provide an appropriate name for each cluster using any or all of the variables in the dataset. 

Cluster-1 - Hold cluster.

Cluster-2 - Hold cluster.

Cluster-3 - Buy Cluster.

Cluster-4 - High Hold cluster.

Cluster-5 - High Hold cluster.
